---
title: "Visual analysis of relocation and trajectory data"
author: "Marius Bottin"
date: "`r Sys.Date()`"
output: 
    github_document:
      number_sections: true
      toc: true
      toc_depth: 4
      dev: 'jpeg'
always_allow_html: true
---


```{r setup, echo=F,message=F,warning=FALSE,results='hide'}
stopifnot(
require(RPostgreSQL)
&
require(rpostgis)
&
require(sp)
&
require(geodata)
&
require(DBI)
&
require(ctmm)
&
require(rgeos)
&
require(leaflet)
&
require(move)
)

knitr::opts_chunk$set(cache=T,tidy.opts = list(width.cutoff = 70), tidy = TRUE, fig.path="Fig/extraDB_",echo=T)
def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  paste0("\n \\", "footnotesize","\n\n", x, "\n\n \\normalsize\n\n")
})
options(knitr.kable.NA = "---")
dirData <- "../../../uwt_repo_data/extra_spatial/"
set.seed(9835)
extraSp<-dbConnect(drv = PostgreSQL(), dbname="move_extra_sp")
# For avoiding setting the connection name in the SQL chunks:
knitr::opts_chunk$set(connection=extraSp)
```

# Loading filtered data

We first load the filtered object containing the data in the `ctmm` and `move` formats, which was created in [outliers.Rmd](../../data_management/local/outliers.md)

```{r}
load("../../data_management/local/filteredList.RData")
```


# Basic maps of relocations
## With leaflet

The map of points and lines with `leaflet` is created that way:
```{r}
llMaps<-lapply(filteredList,function(x)
{
  A<-move2ade(x$moveData)
  res<- leaflet(A) %>%
    addProviderTiles("Esri.WorldImagery") %>%
    addPolylines(data=as(A,"SpatialLines"))%>%
    addCircleMarkers(radius = 1, color = "red",fill = "red")
  return(res)
})

```
### Ardilla1

```{r}
llMaps$Ardilla1
```


### Ardilla2

```{r}
llMaps$Ardilla2
```

### Asio2

```{r}
llMaps$Asio2
```
### BuhoPigua6

```{r}
llMaps$BuhoPigua6
```

### Garza1

```{r}
llMaps$Garza1
```

### GarzaAve2

```{r}
llMaps$GarzaAve2
```

### GarzaAve3

```{r}
llMaps$GarzaAve3
```

### GarzaAve4

```{r}
llMaps$GarzaAve4
```

### GarzaTiti3

```{r}
llMaps$GarzaTiti3
```

### Guacharaca01

```{r}
llMaps$Guacharaca01
```

### Guacharaca02

```{r}
llMaps$Guacharaca02
```

### Guacharaca03

```{r}
llMaps$Guacharaca03
```

### Guacharaca04

```{r}
llMaps$Guacharaca04
```

### Guacharaca06

```{r}
llMaps$Guacharaca06
```

### GuacharacaAsio-4

```{r}
llMaps$`GuacharacaAsio-4`
```

### PavaGarza-4

```{r}
llMaps$`PavaGarza-4`
```

### PavaGuacharaca5

```{r}
llMaps$PavaGuacharaca5
```

### PerezosoZorro1

```{r}
llMaps$PerezosoZorro1
```

### Phimosus01

```{r}
llMaps$Phimosus01
```

### Phimosus02
```{r}
llMaps$Phimosus02
```


### Phimosus03

```{r}
llMaps$Phimosus03
```

### Phimosus04

```{r}
llMaps$Phimosus04
```

### Phimosus05

```{r}
llMaps$Phimosus05
```

### Phimosus06

```{r}
llMaps$Phimosus06
```

### Phimosus07

```{r}
llMaps$Phimosus07
```

### Pigua1

```{r}
llMaps$Pigua1
```

### Pigua2

```{r}
llMaps$Pigua2
```

### Pigua5

```{r}
llMaps$Pigua5
```

### Titi4

```{r}
llMaps$Titi4
```


### Zarigueya1

```{r}
llMaps$Zarigueya1
```

### Zarigueya3

```{r}
llMaps$Zarigueya3
```

### Zarigueya4

```{r}
llMaps$Zarigueya4
```

### Zarigueya5

```{r}
llMaps$Zarigueya5
```

### Zarigueya6

```{r}
llMaps$Zarigueya6
```

### Zarigueya7

```{r}
llMaps$Zarigueya7
```

### Zorro02

```{r}
llMaps$Zorro02
```

### Zorro03

```{r}
llMaps$Zorro03
```

### Zorro04

```{r}
llMaps$Zorro04
```

### Zorro05

```{r}
llMaps$Zorro05
```

### Zorro06

```{r}
llMaps$Zorro06
```

### Zorro07

```{r}
llMaps$Zorro07
```

### Conclusion `leaflet`
`leaflet` gives us the possibility to observe the relocations and trajectory on a satellite basemap.
Moreover, when applied on a local machine, it is possible to zoom into the map to see details.
However, when a lot of points and lines are overlapping, it is quite difficult to distinguish the movement and to extrapolate some patterns out of the maps


