---
title: "Building an analysis plan from the 'movement ecology' literature"
author: "Marius Bottin"
date: "`r Sys.Date()`"
output: 
    github_document:
      toc: true
      toc_depth: 4
      dev: 'jpeg'
always_allow_html: true
bibliography: "./AMVA_movement_ecol.bib"
csl: "./chicago.csl"
---

```{r setup}
knitr::opts_chunk$set(cache=T,tidy.opts = list(width.cutoff = 70), tidy = TRUE, fig.path="Fig/plan",echo=T)
```


In order to create an analysis plan for the animal tracking data in Medellin and the Aburrá valley, we consulted a few recent papers on the subject.
The literature on the topic of movement ecology has considerably increased in the last decade and all authors seem to consider that the recent development in the device designs has boosted the analysis possibilities.

In this document, we will present the potential analyses for our data, accounting for the nature of our data, and the objectives of the project: tracking movement of animals in a large Colombian metropolis, and deducing some implications in terms of ecological connectivity.

# Analyses: literature and possibilities

While the arena is evolving rapidly and the movement data analysis framework is not completely stables, the literature usually separate two main fields of analyses [@Seidel2018;@Demsar2015]:

1. trajectory analyses
1. space-use analyses

Most of the analyses that we can find are dependent on the types and quality of available data [@Edelhoff2016; @Hertel2020; @Thurfjell2014; @Seidel2018].
For example, one of the main challenge in relocation data analysis is to attribute trajectories and locations to particular behaviors of the individuals [e.g. @Seidel2018; @Demsar2015;@Hertel2020].
It is clear that having access to a fine spatial description of the environment, a very frequent and precise relocation dataset, and many individuals from species population is necessary to be able to assess and classify precisely the behaviors of the individuals.
We do not have access in our project to a precise spatial description of the environment in the Metropolitan Area of Medellin (spatial classification of resources), and technical constraints (energy consumption of the GPS collars) do not allow us to have an extremely fine frequency of the relocation data.
However, several analyses are possible to conduct in our dataset.

## Current analyses
The current possibilities explored for our dataset are:

* **Analyses of data errors and outliers through User Equivalent Range Error Model (UERE) calibration** from the `ctmm` package [@Calabrese2016]
* **Calculation of statistics from the clean relocation data and path metrics** [e.g. @Seidel2018]. There are many statistics to be extracted from a relocation dataset [See table 1 in @Seidel2018 for a list of such statistics]
* **Visualization (and visual analyses) of relocation data and trajectories through Space Time Cubes** [@Demsar2015]. One of the main difficulties with relocation and trajectory analyses is that the visualization of such quantities of overlapping data. So, in order to be able to distinguish the data, a simple solution consists in using time as a third dimension.
* **Basic homerange representation** [@Calabrese2016]: homerange analyses are one of the most used analyses for animal movement data. While there are many options to explore in homerange analyses, `ctmm` propose possibilities to automatically apply these analyses in a "basic" batch setup
* **Analysis of the homerange, relocation and path statistics**: Finally, statistics calculated on homerange, relocation and path analyses will be analysed and presented in a last recapitulative document for all individuals


## Analysis flow

```{r fig.height=5, fig.width=5, echo=FALSE,message=F}
require(DiagrammeR)
grViz(diagram = "digraph G {
 subgraph cluster_analyses{
 node [fontname = arial, shape = oval]
  step1 [label = 'Calculating UERE models']
  step2 [label = 'Filtering outliers and potential erroneous data']
  step3 [label = 'Putting extra spatial data in a local database']
  step4 [label = 'Extracting relocation and trajectory statistics']
  step5 [label = 'Visual analysis of trajectories and relocation in 3D Space Time Cubes']
  step6 [label = 'Running homerange models']
  step7 [label = 'Extracting homerange statistics']
  step8 [label = 'Analysing results from previous steps together']
  step9 [label = 'Identifying new research questions']
 label=<<B>Analyses</B>>;
 fontsize=19
  step1 -> step2 -> step3 -> step4 -> step5 -> step6 -> step7 -> step8 -> step9;
 }
 
 node [fontname = Helvetica, shape = tab,style=filled,fillcolor=grey]
 set1 [label = 'Movebank movement dataset',rank=1]
 set2 [label = 'Filtered movement dataset',rank=2]
 set3 [label = 'Extra spatial data',rank=3]
 set4 [label = 'Statistic collection']
 set1 -> set2
 set1 -> step1;
 set1 -> step2;
 step2 -> set2 -> {step4 step5 step6 step8};
 step3 -> set3;
 set3 -> step4;
 set3 -> step5;
 {step4 step7} -> set4 -> step8
 
}

", )
```

## Future potential analyses
In the future, extra-analyses may be applied:

* @Dodge2013 shows how to use the "Env-DATA" system in order to add some environmental data to the movement dataset. If further questions (for example the effect of meterology on the movement behavior of the animals) are to be explored with these dataset, Env-DATA might come in handy!
* @Jeltsch2013a discuss conceptually the relationships between movement ecology and biodiversity ecology. It may be a good reference for going further in the analysis of this dataset in relations to other questions which are developped in the *Instuto Alexander Von Humboldt*









# References