---
title: "Importing, cleaning and formatting data"
author: "Marius Bottin"
date: "`r Sys.Date()`"
output: 
    github_document:
      toc: true
      toc_depth: 4
      dev: 'jpeg'
always_allow_html: true
---


```{r setup, echo=F,message=F,warning=FALSE,results='hide'}
stopifnot(
  require(move)
  &
  require(ctmm)
  &
  require(rgeos)
  )

knitr::opts_chunk$set(cache=T,tidy.opts = list(width.cutoff = 70), tidy = TRUE, fig.path="Fig/icf_",echo=T)
def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  paste0("\n \\", "footnotesize","\n\n", x, "\n\n \\normalsize\n\n")
})
options(knitr.kable.NA = "---")
set.seed(9835)
```

The packages *move* and *ctmm* allow one to import data from the <movebank.org> platform.
Then, various functions are useful to cleaning the imported data and to format it in different object types, specific to the analyses which will be used.

# Importing data
## From movebank with *move*

The data from the <movebank.org> platform might be imported with the package move.
Various functions are used to download the data concerning:

1. the reference data containing the information about the animals, the tags, and the deployments
1. more specific information concerning the animals
1. the relocation data, automatically imported as a "MoveStack" object in R. Note that the data may or may not include the "outliers" defined in movebank depending on the value argument *includeOutliers* in the function call

```{r file="importingMovebankData.R"}
source("importingMovebankData.R")
```

## From a direct call to the movebank API

In order to have more control on the data which is imported from movebank, it is also possible to use directly the movebank API from R, without using the functions from the *move* package.
One of the advantage here is that it is possible to control the type of data in which we want to import the various ids from movebank. Because these ids are sometimes very large integer values, movebank tend to simplify these numbers, and by doing so various ids might be confounded.


```{r file="movebankFromDirectApi.R"}
source("movebankFromDirectApi.R")
```

In the direct API download, we read the tag ids as text, while *move* read them as numbers:

```{r}
# From the move package
head(unique(refData$tag_local_identifier))
length(unique(refData$tag_local_identifier))
# From the controlled API use
head(unique(tracker$supplier_id))
length(unique(tracker$supplier_id))

```

## Itis taxonomy

Movebank uses the Itis taxonomy database to manage taxonomic information.
Our issue here is that some of the species as defined in our study are not registered in the Itis database (*Ortalis columbiana*)

```{r file="itis_taxo.R"}
source("itis_taxo.R")
```
```{r}
kableExtra::kbl(taxo)
```


## Transforming to a ctmm object

The packages `move` and `ctmm` use different class of objects for the movement data, in order to transform `move` objects  to the `ctmm` ones, use the following code:

```{r, message=F, warning=FALSE}
require(ctmm)
ctmmData_clean <- as.telemetry(mvData_clean)
```

# Checking and cleaning data

## Example 1 : Zorro07

### Spatial representation

In order to clean movement (relocation) data sets, there are various tools in movebank, `move` and `ctmm`.
For showing how to apply `move` and `ctmm` functions, we will first focus on one animal: Zorro07

```{r}
mvData_zorro07<-getMovebankData(study = study_id, login = lgin, animalName = "Zorro07")
```

Let's have a first look at the relocation data:

```{r simplezorro07plot}
plot(mvData_zorro07,type="b",pch=16, lwd=.5)
```

Since it is not easy to look at the relocation data without any spatial reference, we may use some external spatial data:


```{r leafletzorro07}
require(leaflet)
leaflet(mvData_zorro07) %>% addProviderTiles("Esri.WorldImagery") %>% addCircleMarkers(radius = 1, color = "red")
```


### Looking at dates and times

The first thing to do is to transform the times to the local timezone:
```{r}
require(lubridate)
timestamps(mvData_zorro07) <- with_tz(timestamps(mvData_zorro07), tz="America/Bogota")
```



```{r}
hist(timestamps(mvData_zorro07),breaks="days",freq=T,las=2, format="%d %b",xlab=NA, main="Number of relocation by date")
```
We can see that there has been a long period without relocation data, between the end of November and the beginning of January, and another small one at the end of January.

Now let's make an histogram of the time of the day of the relocations:

```{r}
# First we extract the hours, min, seconds
hms_t <- lapply(strsplit(format(timestamps(mvData_zorro07),"%H:%M:%S"),":"),as.integer)
# Then we calculate the number of seconds from 00:00, and represent it in a histogram:
hist(sapply(hms_t,function(x)x[3]+(60*x[2])+(3600*x[1])),nclass=500,xaxt="n", xlab="Time", main="Histogram of relocation time")
axis(1,at=seq(0,23*60*60,60*60),paste(0:23,":00",sep=""),las=2)
```

It seems difficult to find the regularity of time in this data, probably because the frequency have been reprogrammed, so we have two frequency regimes mixed in the data.


### Calibration with ctmm

In order to calibrate the devices for coordinates errors, we use datasets of locations that were obtained in the places where the devices were stocked before their deployments. 
These calibration datasets are downloaded in the movebank format.
Then a "User Equivalent Range Error" model is made with the function uere.fit:

```{r}
calibData_zorro07<-as.telemetry("../../../uwt_repo_data/calibration/Zorro7.csv")
plot(calibData_zorro07)
UERE<-uere.fit(calibData_zorro07)
```

Then the model is applied to the telemetry data after deployment:


```{r}
ctmm_zorro07<-as.telemetry(mvData_zorro07)
uere(ctmm_zorro07) <- UERE
```

In the following graph, location are represented in a red scale depending on their distance to the previous location, and a blue scale represent the average speed of the trajectories

```{r}
plot(ctmm_zorro07,error=2)
```


`ctmm` allows then to find outliers, based on these error and the calculation of average speed of the individual between 2 relocations.


```{r}
outlie(ctmm_zorro07) -> OUT
plot(OUT,units=F)
```

In this particular case, there is no particularly clear outlier (note that the highest average velocity correspond to 0.3 $m.s^{-1}$, or approx. 1 $km.h^{-1}$).


<!--
```r
require(parallel)
GUESS<-ctmm.guess(ctmm_zorro07,CTMM=ctmm(error=T),interactive = F)
FIT<-ctmm.select(ctmm_zorro07,GUESS,trace=T, cores=0)
```

```r
save(list=c("GUESS","FIT"),file="ctmm_zorro07.RData")
```

-->

## Example 2 : GarzaAve4

### Spatial representation

GarzaAve4 was a simple example, for which the automatic filters from movebank seem to have exclude all the outliers.
Now we will look at another example


```{r}
mvData_garzaAve4<-getMovebankData(study = study_id, login = lgin, animalName = "GarzaAve4")
```

Let's have a first look at the relocation data:

```{r simplegarzaAve4plot}
plot(mvData_garzaAve4,type="b",pch=16, lwd=.5)
```

Since it is not easy to look at the relocation data without any spatial reference, we may use some external spatial data:


```{r leafletgarzaAve4}
require(leaflet)
leaflet(mvData_garzaAve4) %>% addProviderTiles("Esri.WorldImagery") %>% addCircleMarkers(radius = 1, color = "red")
```


### Looking at dates and times

The first thing to do is to transform the times to the local timezone:
```{r}
require(lubridate)
timestamps(mvData_garzaAve4) <- with_tz(timestamps(mvData_garzaAve4), tz="America/Bogota")
```



```{r}
hist(timestamps(mvData_garzaAve4),breaks="days",freq=T,las=2, format="%d %b",xlab=NA, main="Number of relocation by date")
```
We can see that there has been a long period without relocation data, between the end of November and the beginning of January, and another small one at the end of January.

Now let's make an histogram of the time of the day of the relocations:

```{r}
# First we extract the hours, min, seconds
hms_t <- lapply(strsplit(format(timestamps(mvData_garzaAve4),"%H:%M:%S"),":"),as.integer)
# Then we calculate the number of seconds from 00:00, and represent it in a histogram:
hist(sapply(hms_t,function(x)x[3]+(60*x[2])+(3600*x[1])),nclass=500,xaxt="n", xlab="Time", main="Histogram of relocation time")
axis(1,at=seq(0,23*60*60,60*60),paste(0:23,":00",sep=""),las=2)
```

It seems difficult to find the regularity of time in this data, probably because the frequency have been reprogrammed, so we have two frequency regimes mixed in the data.


### Calibration with ctmm

In order to calibrate the devices for coordinates errors, we use datasets of locations that were obtained in the places where the devices were stocked before their deployments. 
These calibration datasets are downloaded in the movebank format.
Then a "User Equivalent Range Error" model is made with the function uere.fit:

```{r}
calibData_garzaAve4<-as.telemetry("../../../uwt_repo_data/calibration/Zorro7.csv")
plot(calibData_garzaAve4)
UERE<-uere.fit(calibData_garzaAve4)
```

Then the model is applied to the telemetry data after deployment:


```{r}
ctmm_garzaAve4<-as.telemetry(mvData_garzaAve4)
uere(ctmm_garzaAve4) <- UERE
```


```{r}
plot(ctmm_garzaAve4,error=2)
```

In the following graph, location are represented in a red scale depending on their distance to the previous location, and a blue scale represent the average speed of the trajectories


`ctmm` allows then to find outliers, based on these error and the calculation of average speed of the individual between 2 relocations.

```{r}
outlie(ctmm_garzaAve4) -> OUT
plot(OUT,units=F)
```

In this particular case, there is no particularly clear outlier (note that the highest average velocity correspond to 0.3 $m.s^{-1}$, or approx. 1 $km.h^{-1}$).


<!--
```r
require(parallel)
GUESS<-ctmm.guess(ctmm_garzaAve4,CTMM=ctmm(error=T),interactive = F)
FIT<-ctmm.select(ctmm_garzaAve4,GUESS,trace=T, cores=0)
```

```r
save(list=c("GUESS","FIT"),file="ctmm_garzaAve4.RData")
```

-->

##