---
title: "Creating a local database of extra spatial data to be associated with movement data"
author: "Marius Bottin"
date: "`r Sys.Date()`"
output: 
    github_document:
      toc: true
      toc_depth: 4
      dev: 'jpeg'
always_allow_html: true
---


In order to do analyses of movement data, it may be useful to have a database running a spatial data-management system.
Here I will use a postgres database with the postgis extension (I run already various databases with this setup on my computer).
However, in most of the case, you will find the spatialite extension of SQLite more adequate at the scale of one study, particularly when all the analyses are made in a single computer.

The main advantages of having a local database with spatial data are:

1. all the data can be accessed from a same source, and in the same way
1. you can control and check efficiently the projections used and the structure of the spatial data

**********************

**Note**:

A large part of the extra data that we will use here are not yet public, so I won't be able to share them.
When the files are public, the code will include the downloading with wget, or sometimes directly in R.
My personal setup for this data consists in a folder called "uwt_data_repo" which shares the same root as this repository.
Local files are copied to this folder.



**********************

```{r setup, echo=F,message=F,warning=FALSE,results='hide'}
stopifnot(
require(RPostgreSQL)
&
require(rpostgis)
&
require(sp)
&
require(geodata)
&
require(DBI)
)

knitr::opts_chunk$set(cache=T,tidy.opts = list(width.cutoff = 70), tidy = TRUE, fig.path="Fig/extraDB_",echo=T)
def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  paste0("\n \\", "footnotesize","\n\n", x, "\n\n \\normalsize\n\n")
})
options(knitr.kable.NA = "---")
dirData <- "../../../uwt_repo_data/extra_spatial/"
set.seed(9835)
```

# Creating the database

In bash, if you have postgreSQL installed, one of the easiest solution to create a database is:

```bash
createdb move_extra_sp
```

Then, I recommend the use of [pgpass](https://www.postgresql.org/docs/current/libpq-pgpass.html).
I mainly use it because I can connect to the database without sharing the connection passwords here, but the fact that it avoids the need to enter hosts and password without decreasing significantly the security of the connection may be appealing to anyone.

Then we create the connection for accessing it from R:

```{r, cache=F}
extraSp<-dbConnect(drv = PostgreSQL(), dbname="move_extra_sp")
# For avoiding setting the connection name in the SQL chunks:
knitr::opts_chunk$set(connection=extraSp)
```


We will check on the installation of the postgis extension and if needed, install it

```{r}
pgPostGIS(extraSp)
```
Now for the postgis_raster extension:
```{r}
ext <- dbGetQuery(conn = extraSp, "SELECT * FROM pg_available_extensions;")
if(is.na(ext[ext$name=="postgis_raster","installed_version"]))
{
  dbSendQuery(extraSp,"CREATE EXTENSION postgis_raster")
}
```

Finally, we will create a schema to put all the raw data:

```{r}
if(!"rawdata"%in%dbGetQuery(extraSp,"SELECT schema_name FROM information_schema.schemata")$schema_name)
{dbSendQuery(extraSp,"CREATE SCHEMA rawdata;")}
```


# Administrative boundaries

It is always useful to have access to administrative boundaries from the country you are working in.
[GADM](https://gadm.org/) is an opensource initiative which allows to download this kind of data.
In R, it is directly available through the [geodata](https://github.com/rspatial/geodata/) package.


Let's download the data in a temporary folder and insert it in its raw form in the database:
```{r, message=F, eval=!dbExistsTable(extraSp,"mpio")}
tmp <- tempdir()
municipios <- as(gadm("Colombia", level=2, path= tmp),"Spatial")
pgInsert(extraSp,c("rawdata","municipios"),municipios,geom="the_geom",overwrite = T)
```


```{sql eval = !dbExistsTable(extraSp,"mpio")}
CREATE TABLE mpio
(
    mpio_id smallserial PRIMARY KEY,
    country varchar(3) NOT NULL,
    dept text NOT NULL,
    mpio text NOT NULL,
    mpio_syno TEXT[]
);
SELECT AddGeometryColumn ('public','mpio','the_geom',4326,'MULTIPOLYGON',2);
CREATE INDEX idx_mpio_the_geom ON mpio USING GIST(the_geom);
INSERT INTO mpio(country,dept,mpio,mpio_syno,the_geom)
SELECT "GID_0","NAME_1", "NAME_2",STRING_TO_ARRAY("VARNAME_2",'|'),the_geom
FROM rawdata.municipios
ORDER BY "NAME_1","NAME_2"
RETURNING mpio.dept, mpio.mpio, mpio.mpio_syno;
```


The map can be called in R directly now, for example, to load all the municipalities from the "Antioquia" department:
```{r muni_plot}
antioquiaMunic <- pgGetGeom(extraSp, query= "SELECT * FROM mpio WHERE dept='Antioquia'",geom = "the_geom")
plot(antioquiaMunic)
plot(antioquiaMunic[antioquiaMunic$mpio=="Medellín",], col="red",add=T)
```



# Rasters from connectivity analyses

## Circuit theory

Among the spatial data associated with this project, a model of connectivity based on circuit theory was provided by `TODO: find who made the model`.

The file containing the resulting data is the file "Circuitos_electricos.tif" analysed here with gdalinfo:

```{bash}
gdalinfo ../../../uwt_repo_data/extra_spatial/Circuitos_electricos.tif
```

The important information that we can gather from gdalinfo are:

* the projection system: MAGNAS-SIRGAS/Colombia Bogotá Zone (SRID: 3116)
* the range of value from the pixel: 1 to 10
* the NoData value: 15

First we re-project the data to the SRID 4326 (WGS84) which is the usual projection system from the data we will obtain from movebank:

```{bash, eval=!dbExistsTable(extraSp,"circ_theory")}
gdalwarp -t_srs EPSG:4326 ../../../uwt_repo_data/extra_spatial/Circuitos_electricos.tif ../../../uwt_repo_data/extra_spatial/Circuitos_electricos_wgs84.tif
```



In order to include the table containing this data in the database, we use the following bash command:

```{bash eval=!dbExistsTable(extraSp,"circ_theory")}
raster2pgsql -c -N 15 -s 4326 -I -C -M ../../../uwt_repo_data/extra_spatial/Circuitos_electricos_wgs84.tif -t 100x100 -f the_rast -q circ_theory | psql move_extra_sp -b > /dev/null
rm ../../../uwt_repo_data/extra_spatial/Circuitos_electricos_wgs84.tif
```

The raster can be called in R using:
```{r circuit_theory_plot}
ct_rast <- pgGetRast(conn = extraSp, name="circ_theory", rast="the_rast")
plot(ct_rast)
```



## Least cost path

Another connectivity model was run to create a least cost path raster, in which the values of the raster represent the connectivity "cost".

The file containing the resulting data is the file "RutasMenorCosto.tif" analysed here with gdalinfo:

```{bash}
gdalinfo ../../../uwt_repo_data/extra_spatial/RutasMenorCosto.tif
```

The important information that we can gather from gdalinfo are:

* the projection system: Transverse mercator MAGNAS-SIRGAS/Colombia Bogotá Zone (SRID: 4686 ... not sure!)
* the range of value from the pixel: 1 to 10
* the NoData value: -2147483647

First we re-project the data to the SRID 4326 (WGS84) which is the usual projection system from the data we will obtain from movebank:

```{bash, eval=!dbExistsTable(extraSp,"least_cost")}
gdalwarp -t_srs EPSG:4326 ../../../uwt_repo_data/extra_spatial/RutasMenorCosto.tif ../../../uwt_repo_data/extra_spatial/RutasMenorCosto_wgs84.tif
```



In order to include the table containing this data in the database, we use the following bash command:

```{bash eval=!dbExistsTable(extraSp,"least_cost")}
raster2pgsql -c -N -2147483647 -s 4326 -I -C -M ../../../uwt_repo_data/extra_spatial/RutasMenorCosto_wgs84.tif -t 100x100 -f the_rast -q least_cost | psql move_extra_sp -b > /dev/null
rm ../../../uwt_repo_data/extra_spatial/RutasMenorCosto_wgs84.tif
```

The raster can be called in R using:
```{r least_cost_plot}
lc_rast <- pgGetRast(conn = extraSp, name="least_cost", rast="the_rast")
plot(lc_rast)
```



## Node degree

Another connectivity model was run to create a node degree calculation for green area in the metropolitan area. I am not yet sure what represent exactly the values between the green areas...

The file containing the resulting data is the file "GradoNodal.tif" analysed here with gdalinfo:

```{bash}
gdalinfo ../../../uwt_repo_data/extra_spatial/GradoNodal.tif
```

The important information that we can gather from gdalinfo are:

* the projection system: MAGNAS-SIRGAS/Colombia Bogotá Zone (SRID: 3116 ... not sure!)
* the range of value from the pixel: 1 to 10
* the NoData value: 255

First we re-project the data to the SRID 4326 (WGS84) which is the usual projection system from the data we will obtain from movebank:

```{bash, eval=!dbExistsTable(extraSp,"node_deg")}
gdalwarp -t_srs EPSG:4326 ../../../uwt_repo_data/extra_spatial/GradoNodal.tif ../../../uwt_repo_data/extra_spatial/GradoNodal_wgs84.tif
```



In order to include the table containing this data in the database, we use the following bash command:

```{bash eval=!dbExistsTable(extraSp,"node_deg")}
raster2pgsql -c -N 255 -s 4326 -I -C -M ../../../uwt_repo_data/extra_spatial/GradoNodal_wgs84.tif -t 100x100 -f the_rast -q node_deg | psql move_extra_sp -b > /dev/null
rm ../../../uwt_repo_data/extra_spatial/GradoNodal_wgs84.tif
```

For some reason this raster has been encoded in a way that makes it impossible to load in R memory. Theoretically, it would be possible (if the raster was not that heavy) to apply:
```r
nd_rast <- pgGetRast(conn = extraSp, name="node_deg", rast="the_rast")
plot(nd_rast)
```

TODO: It appears that the error comes from a problematic handling of the noData value, which seems to be the case in qgis as well...

# Human pressure index

A human pressure index was calculated on the metropolitan area (IHEH, Correa et al. 2020)

The file containing the resulting data is the file "IHEH_2019_AMVA.tif" analysed here with gdalinfo:

```{bash}
gdalinfo ../../../uwt_repo_data/extra_spatial/IHEH_2019_AMVA.tif
```

The important information that we can gather from gdalinfo are:

* the projection system: Transverse mercator MAGNAS-SIRGAS/Colombia Bogotá Zone (SRID: 4686 ... not sure!)
* the range of value from the pixel: 1 to 100
* the NoData value: -3.40282e+38

First we re-project the data to the SRID 4326 (WGS84) which is the usual projection system from the data we will obtain from movebank:

```{bash, eval=!dbExistsTable(extraSp,"iheh")}
gdalwarp -t_srs EPSG:4326 ../../../uwt_repo_data/extra_spatial/IHEH_2019_AMVA.tif ../../../uwt_repo_data/extra_spatial/IHEH_2019_AMVA_wgs84.tif
```



In order to include the table containing this data in the database, we use the following bash command:

```{bash eval=!dbExistsTable(extraSp,"iheh")}
raster2pgsql -c -N -3.40282e+38 -s 4326 -I -C -M ../../../uwt_repo_data/extra_spatial/IHEH_2019_AMVA_wgs84.tif -t 100x100 -f the_rast -q iheh | psql move_extra_sp -b > /dev/null
rm ../../../uwt_repo_data/extra_spatial/IHEH_2019_AMVA_wgs84.tif
```

The raster can be called in R using:
```{r iheh_plot}
iheh_rast <- pgGetRast(conn = extraSp, name="iheh", rast="the_rast")
plot(iheh_rast)
```

# Turning off the light and leaving

```{r}
dbDisconnect(extraSp)
```