---
title: "Spatial error calibration"
author: "Marius Bottin"
date: "`r Sys.Date()`"
output: 
    github_document:
      toc: true
      toc_depth: 4
      dev: 'jpeg'
      df_print: "kable"
always_allow_html: true
---


```{r setup, echo=F,message=F,warning=FALSE,results='hide'}
stopifnot(
require(move)
  &
require(ctmm)
  &
require(rgeos)
&
require(kableExtra)
&
require(leaflet)
  )

knitr::opts_chunk$set(cache=T,tidy.opts = list(width.cutoff = 70), tidy = TRUE, fig.path="Fig/calib_",echo=T)
def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  paste0("\n \\", "footnotesize","\n\n", x, "\n\n \\normalsize\n\n")
})
options(knitr.kable.NA = "---")
set.seed(9835)
```


Telemetry data from movebank comes with the HDOP measurement of GPS errors.
This measurement, however does not give the real error in meter.
In order to make it interpretable, it should be accompanied by a User Equivalent Range Error (UERE).
The `ctmm` package propose to fit the UERE with a calibration dataset.
Thus, calibrated data should be used to extract an estimation of spatial error in each point.
However, the documentation on how to do that is not very clear.
In this document, I will explore the calibration process in `ctmm`, in order to better understand how to manage the errors later.

# Getting main information from movebank


We first import movebank data, to get the information about animals and deployment, in case they are useful later...

See corresponding R files and/or [importingCleaningFormatting.Rmd](importingCleaningFormatting.md) for more information.

```{r}
source(file = "./importingMovebankData.R")
```



# Importing Calibration data

The calibration data consist in a set of csv files in the movebank csv export format, before deployment, in a place where devices where stored without moving during a period.

```{r}
folCalib<-"../../../uwt_repo_data/calibration/"
(calibFiles<-dir(folCalib,pattern="csv"))
#read.csv files
CSV_calib<-lapply(paste0(folCalib,calibFiles),read.csv,sep=";")
names(CSV_calib)<-gsub("\\.csv$","",calibFiles)
```

## Correcting errors in the calibration files

There are various errors in the calibration files. My guess is that they have been created and/or modified in Excel (which almost always results in errors).

### Dealing with wrong names

The names of the animals are wrong in the files, so we will have to modify them to avoid errors.

The first thing to do is to find the correspondance between movebank names and the calibration files:

```{r}
aniNames <- animals$local_identifier[animals$number_of_events>20]
# The calibration files do not have exactly the same names as the animals
caliNames <- gsub("\\.csv","",dir("../../../uwt_repo_data/calibration/",pattern="csv"))

tabNames <- data.frame(
  aniNames=aniNames,
  partLetter=gsub("-","",gsub("^([-A-Za-z]+)([0-9]+)$","\\1",aniNames)),
  partNumber=as.integer(gsub("^([-A-Za-z]+)([0-9]+)$","\\2",aniNames)),
  calibName=NA
)
matches <- sapply(caliNames,function(x,tab)
  {
    let <- gsub("^([A-Za-z]+)([0-9]+$)","\\1",x)
    num <- gsub("^([A-Za-z]+)([0-9]+$)","\\2",x)
    which((tab$partLetter==let|(tab$partLetter=="GarzaAve"&let=="Garza"))&tab$partNumber==num)
  }, tab=tabNames)
tabNames$calibName[matches]<-caliNames
kable(tabNames[c("aniNames","calibName")],colnames=c("Movebank name","Calibration file name"))
```


We now replace the names in the data imported from the CSV files:

```{r}
m_names <- match(names(CSV_calib),tabNames$calibName)
(m_movebank_names<-tabNames[m_names,"aniNames"])
names(CSV_calib) <- m_movebank_names
for(i in 1:length(CSV_calib)){
  CSV_calib[[i]]$individual.local.identifier<-m_movebank_names[i]
}
```

### Errors in coordinates


The coordinates of many of the calibration files are wrong in their digits. For example, *Garza1*
```{r}
head(CSV_calib$Garza1[c("location.long","location.lat")])
```

It is the case for:

```{r}
(pbCoord<-sapply(CSV_calib,function(x)is.character(x$location.long)|is.character(x$location.lat)))
```

It may be corrected with the following code:

```{r}
for(i in 1:length(CSV_calib))
{
  if(pbCoord[i])
  {
    if(is.character(CSV_calib[[i]]$location.long)){
      CSV_calib[[i]]$location.long<-as.numeric(gsub("^-75","-75.",gsub("\\.","",CSV_calib[[i]]$location.long)))
    }
    if(is.character(CSV_calib[[i]]$location.lat)){
      CSV_calib[[i]]$location.lat<-as.numeric(gsub("^6","6.",gsub("\\.","",CSV_calib[[i]]$location.lat)))
    }
  }
}
```

## Getting the calibration data in `ctmm` format

Then, when the errors are fixed, we can transform it as a  `ctmm` object:

```{r warning=FALSE, message=FALSE}
calibData <- lapply(CSV_calib,as.telemetry)
```
# Analysing calibration data

## Main informations
We can calculate statistics on the calibration data:

```{r}
nbPoints <- sapply(calibData,function(x)nrow(x))
calibDistPoints <- lapply(calibData,function(x)gDistance(SpatialPointsDataFrame.telemetry(x),byid=T))
calibConvexHull <- lapply(calibData,function(x)gConvexHull(SpatialPointsDataFrame.telemetry(x)))
data.frame(
  nbPoints = nbPoints,
  average = sapply(calibDistPoints,function(x)mean(as.dist(x))),
  min = sapply(calibDistPoints,function(x)min(as.dist(x))),
  max = sapply(calibDistPoints,function(x)max(as.dist(x))),
  areaChull = sapply(calibConvexHull,gArea),
  hdop_aver = sapply(calibData,function(x)mean(x$HDOP)),
  hdop_min = sapply(calibData,function(x)min(x$HDOP)),
  hdop_max = sapply(calibData,function(x)max(x$HDOP))
)%>%
  kable(col.names = c("Number of points","Average","Minimum","Maximum","Area","Average","Minimum","Maximum"))%>%
  add_header_above(c(" "=2,"Distance between calibration points (m)"=3,"Convex hull (m2)"=1,"HDOP"=3))
```


## Maps of calibration data

**Garza1**:

```{r ll_calib_garza1,warning=F}

  leaflet(spTransform(SpatialPointsDataFrame.telemetry(calibData[["Garza1"]]),CRS("+proj=longlat +datum=WGS84"))) %>% addProviderTiles("Esri.WorldImagery") %>%
  addPolygons(data=spTransform(calibConvexHull$Garza1,CRS("+proj=longlat +datum=WGS84")))%>%
  addCircleMarkers(radius = 1, color = "red",fill = "red")
```


**GarzaAve4**:

```{r ll_calib_garzaave4,warning=F}

  leaflet(spTransform(SpatialPointsDataFrame.telemetry(calibData[["GarzaAve4"]]),CRS("+proj=longlat +datum=WGS84"))) %>% addProviderTiles("Esri.WorldImagery") %>%
  addPolygons(data=spTransform(calibConvexHull$GarzaAve4,CRS("+proj=longlat +datum=WGS84")))%>%
    addCircleMarkers(radius = 1, color = "red",fill = "red")
```


**Guacharaca01**:

```{r ll_calib_Guacharaca01,warning=F}

  leaflet(spTransform(SpatialPointsDataFrame.telemetry(calibData[["Guacharaca01"]]),CRS("+proj=longlat +datum=WGS84"))) %>% addProviderTiles("Esri.WorldImagery") %>%
  addPolygons(data=spTransform(calibConvexHull$Guacharaca01,CRS("+proj=longlat +datum=WGS84")))%>%
    addCircleMarkers(radius = 1, color = "red",fill = "red")
```


**Guacharaca03**:

```{r ll_calib_Guacharaca03,warning=F}

  leaflet(spTransform(SpatialPointsDataFrame.telemetry(calibData[["Guacharaca03"]]),CRS("+proj=longlat +datum=WGS84"))) %>% addProviderTiles("Esri.WorldImagery") %>%
  addPolygons(data=spTransform(calibConvexHull$Guacharaca03,CRS("+proj=longlat +datum=WGS84")))%>%
    addCircleMarkers(radius = 1, color = "red",fill = "red")
```


**Phimosus02**:

```{r ll_calib_Phimosus02,warning=F}

  leaflet(spTransform(SpatialPointsDataFrame.telemetry(calibData[["Phimosus02"]]),CRS("+proj=longlat +datum=WGS84"))) %>% addProviderTiles("Esri.WorldImagery") %>%
  addPolygons(data=spTransform(calibConvexHull$Phimosus02,CRS("+proj=longlat +datum=WGS84")))%>%
    addCircleMarkers(radius = 1, color = "red",fill = "red")
```


**Phimosus04**:

```{r ll_calib_Phimosus04,warning=F}

  leaflet(spTransform(SpatialPointsDataFrame.telemetry(calibData[["Phimosus04"]]),CRS("+proj=longlat +datum=WGS84"))) %>% addProviderTiles("Esri.WorldImagery") %>%
  addPolygons(data=spTransform(calibConvexHull$Phimosus04,CRS("+proj=longlat +datum=WGS84")))%>%
    addCircleMarkers(radius = 1, color = "red",fill = "red")
```


**Pigua2**:


```{r ll_calib_Pigua2,warning=F}

  leaflet(spTransform(SpatialPointsDataFrame.telemetry(calibData[["Pigua2"]]),CRS("+proj=longlat +datum=WGS84"))) %>% addProviderTiles("Esri.WorldImagery") %>%
  addPolygons(data=spTransform(calibConvexHull$Pigua2,CRS("+proj=longlat +datum=WGS84")))%>%
    addCircleMarkers(radius = 1, color = "red",fill = "red")
```

**Zarigueya1**:

```{r ll_calib_Zarigueya1,warning=F}

  leaflet(spTransform(SpatialPointsDataFrame.telemetry(calibData[["Zarigueya1"]]),CRS("+proj=longlat +datum=WGS84"))) %>% addProviderTiles("Esri.WorldImagery") %>%
  addPolygons(data=spTransform(calibConvexHull$Zarigueya1,CRS("+proj=longlat +datum=WGS84")))%>%
    addCircleMarkers(radius = 1, color = "red",fill = "red")
```


**Zarigueya2**:

```{r ll_calib_Zarigueya2,warning=F}

  leaflet(spTransform(SpatialPointsDataFrame.telemetry(calibData[["Zarigueya2"]]),CRS("+proj=longlat +datum=WGS84"))) %>% addProviderTiles("Esri.WorldImagery") %>%
  addPolygons(data=spTransform(calibConvexHull$Zarigueya2,CRS("+proj=longlat +datum=WGS84")))%>%
    addCircleMarkers(radius = 1, color = "red",fill = "red")
```


**Zarigueya3**:

```{r ll_calib_Zarigueya3,warning=F}

  leaflet(spTransform(SpatialPointsDataFrame.telemetry(calibData[["Zarigueya3"]]),CRS("+proj=longlat +datum=WGS84"))) %>% addProviderTiles("Esri.WorldImagery") %>%
  addPolygons(data=spTransform(calibConvexHull$Zarigueya3,CRS("+proj=longlat +datum=WGS84")))%>%
    addCircleMarkers(radius = 1, color = "red",fill = "red")
```


**Zarigueya4**:

```{r ll_calib_Zarigueya4,warning=F}

  leaflet(spTransform(SpatialPointsDataFrame.telemetry(calibData[["Zarigueya4"]]),CRS("+proj=longlat +datum=WGS84"))) %>% addProviderTiles("Esri.WorldImagery") %>%
  addPolygons(data=spTransform(calibConvexHull$Zarigueya4,CRS("+proj=longlat +datum=WGS84")))%>%
    addCircleMarkers(radius = 1, color = "red",fill = "red")
```


**Zorro02**:


```{r ll_calib_Zorro02,warning=F}

  leaflet(spTransform(SpatialPointsDataFrame.telemetry(calibData[["Zorro02"]]),CRS("+proj=longlat +datum=WGS84"))) %>% addProviderTiles("Esri.WorldImagery") %>%
  addPolygons(data=spTransform(calibConvexHull$Zorro02,CRS("+proj=longlat +datum=WGS84")))%>%
    addCircleMarkers(radius = 1, color = "red",fill = "red")
```

**Zorro03**:

```{r ll_calib_Zorro03,warning=F}

  leaflet(spTransform(SpatialPointsDataFrame.telemetry(calibData[["Zorro03"]]),CRS("+proj=longlat +datum=WGS84"))) %>% addProviderTiles("Esri.WorldImagery") %>%
  addPolygons(data=spTransform(calibConvexHull$Zorro03,CRS("+proj=longlat +datum=WGS84")))%>%
    addCircleMarkers(radius = 1, color = "red",fill = "red")
```


**Zorro04**:

```{r ll_calib_Zorro04,warning=F}

  leaflet(spTransform(SpatialPointsDataFrame.telemetry(calibData[["Zorro04"]]),CRS("+proj=longlat +datum=WGS84"))) %>% addProviderTiles("Esri.WorldImagery") %>%
  addPolygons(data=spTransform(calibConvexHull$Zorro04,CRS("+proj=longlat +datum=WGS84")))%>%
    addCircleMarkers(radius = 1, color = "red",fill = "red")
```


**Zorro05**:

```{r ll_calib_Zorro05,warning=F}

  leaflet(spTransform(SpatialPointsDataFrame.telemetry(calibData[["Zorro05"]]),CRS("+proj=longlat +datum=WGS84"))) %>% addProviderTiles("Esri.WorldImagery") %>%
  addPolygons(data=spTransform(calibConvexHull$Zorro05,CRS("+proj=longlat +datum=WGS84")))%>%
    addCircleMarkers(radius = 1, color = "red",fill = "red")
```


**Zorro06**:


```{r ll_calib_Zorro06,warning=F}

  leaflet(spTransform(SpatialPointsDataFrame.telemetry(calibData[["Zorro06"]]),CRS("+proj=longlat +datum=WGS84"))) %>% addProviderTiles("Esri.WorldImagery") %>%
  addPolygons(data=spTransform(calibConvexHull$Zorro06,CRS("+proj=longlat +datum=WGS84")))%>%
    addCircleMarkers(radius = 1, color = "red",fill = "red")
```

**Zorro07**:


```{r ll_calib_Zorro07,warning=F}

  leaflet(spTransform(SpatialPointsDataFrame.telemetry(calibData[["Zorro07"]]),CRS("+proj=longlat +datum=WGS84"))) %>% addProviderTiles("Esri.WorldImagery") %>%
  addPolygons(data=spTransform(calibConvexHull$Zorro07,CRS("+proj=longlat +datum=WGS84")))%>%
    addCircleMarkers(radius = 1, color = "red",fill = "red")
```


# Getting the movebank data, animal by animal

```{r message=F, warning=F}
rawList <- list()
for(i in 1:nrow(tabNames))
{
  rawList[[tabNames$aniNames[i]]]<-list()
  rawList[[i]]$moveData=getMovebankData(study = study_id, login = lgin,animalName = tabNames$aniNames[i])
  rawList[[i]]$ctmmData=as.telemetry(rawList[[i]]$moveData)
}
```

# Calculating UERE

The User Equivalent Range Error (UERE) correspond to the homoskedastic (i.e. it does not vary as a function of time) part of a location error model.
The Dilution Of Precision (DOP) correspond to the heteroskedastic (i.e. it does vary through time) part of the location error model, and it is usually given for each relocation of a movement dataset.

$location~error(t)= DOP(t) × UERE(t)$

Calculating UERE is done in `ctmm` using a calibration dataset.

```{r}
UERE_list <- lapply(calibData,uere.fit)
```

When you look at the `ctmm` telemetry object of Zorro02 before applying the UERE calibration, for instance:

```{r}
zorro02_ctmm<-rawList$Zorro02$ctmmData
head(zorro02_ctmm)%>%kable()
```

Now, we apply the UERE:
```{r}
uere(zorro02_ctmm)<-UERE_list$Zorro02
head(zorro02_ctmm)%>%kable()
```

As you can see there are now new columns in the table, among which *"VAR.xy"* represent the variation (or the error) on the horizontal dimensions.


The square root of the *"VAR.xy"* variable is linearly dependent of the *HDOP*:

```{r}
plot(zorro02_ctmm$HDOP,sqrt(zorro02_ctmm$VAR.xy),main="Zorro02",xlab="HDOP",ylab="VAR.xy")
```

So this linear relationship may be described by a linear model such as:

```{r}
(LM_errorZorro02<-lm(sqrt(zorro02_ctmm$VAR.xy)~zorro02_ctmm$HDOP))
```

Now if we apply the same treatment to another animal:

```{r}
zarigueya2_ctmm<-rawList$Zarigueya2$ctmmData
uere(zarigueya2_ctmm)<-UERE_list$Zarigueya2
plot(zarigueya2_ctmm$HDOP,sqrt(zarigueya2_ctmm$VAR.xy),main="zarigueya2",xlab="HDOP",ylab="VAR.xy")
(LM_errorzarigueya2<-lm(sqrt(zarigueya2_ctmm$VAR.xy)~zarigueya2_ctmm$HDOP))
```


I believe we should obtain a different factor, however both model give exactly the same slope, only the intercept is different.

It might be that I do not get something in the calibration process, but to be sure I'll send an issue to ctmm-initiative/ctmm...


