---
title: "Managing temporal factors, frequencies of relocations and time lags"
author: "Marius Bottin"
date: "`r Sys.Date()`"
output: 
    github_document:
      toc: true
      toc_depth: 2
      dev: 'jpeg'
always_allow_html: true
---


```{r setup, echo=F,message=F,warning=FALSE,results='hide'}
stopifnot(
require(RPostgreSQL)
&
require(rpostgis)
&
require(sp)
&
require(geodata)
&
require(DBI)
&
require(ctmm)
&
require(move)
&
require(rgeos)
&
require(lubridate)
&
require(leaflet)
&
require(kableExtra)
)

knitr::opts_chunk$set(cache=T,tidy.opts = list(width.cutoff = 70), tidy = TRUE, fig.path="Fig/temporal",echo=T)
def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  paste0("\n \\", "footnotesize","\n\n", x, "\n\n \\normalsize\n\n")
})
options(knitr.kable.NA = "---")
dirData <- "../../../uwt_repo_data/extra_spatial/"
set.seed(9835)
extraSp<-dbConnect(drv = PostgreSQL(), dbname="move_extra_sp")
# For avoiding setting the connection name in the SQL chunks:
knitr::opts_chunk$set(connection=extraSp)
```


# Loading filtered data, by individual

Before doing that, make sure that you ran the code contained in file [SpatialErrorCalibration.Rmd](SpatialErrorCalibration.md).
Various processes needed to be done, in particular the relationship between names of the animals in the movebank data and the calibration local datasets.


We will load the filtered data list created in [outliers.Rmd](./outliers.md)

```{r message=F, warning=F}
load("./filteredList.RData")
```


# Timestamps as a link between relocation data from `move` and `ctmm`

As you may see in the following code, timestamps can be an efficient way to see the correspondences between relocation data in the `move` and `ctmm` format:

```{r}
match(filteredList$Zorro02$moveData$timestamp,filteredList$Zorro02$ctmmData$timestamp)
```
# Checking frequencies and timelags

## Extracting dates and time of relocations

We first extract information for dates and times for every individual:

```{r}
list_dateTime<-lapply(filteredList,function(x)
  data.frame(timestamp=timestamps(x$moveData),
            date=date(timestamps(x$moveData)),
             time=format(timestamps(x$moveData), "%H:%M:%S"),
            time_s=as.numeric(timestamps(x$moveData)) - as.numeric(as.POSIXct(paste0(date(timestamps(x$moveData)), " 00:00:00"))),
            timeLag_s=c(NA, timeLag(x$moveData,"secs"))
  ))
```

Concretely, for each individual, we obtain this table (example: Zorro02, 20 first lines):

```{r}
list_dateTime$Zorro02 %>% head(n=20) %>% kable()
```



## Individual by individual
### Functions

First we define a function which makes easily histograms out of the timestamp information tables, by date and by time of day
```{r}
hists_timestamps<-function(ts_tab, indName=NULL)
{
  par(mar=c(7,4,3,1))
  hist(ts_tab$timestamp,breaks="days", freq=T, main=ifelse(!is.null(indName), paste(indName,": Dates",sep=""), "Dates"), xlab = "Date",las=2)
  hist(ts_tab$time_s,xaxt="n",nclass=100, main = ifelse(!is.null(indName),paste(indName,": Time of day",sep=""), "Dates"), xlab = "Time of day")
  axis(1,at=seq(0,23*60*60,60*60),paste(0:23,":00",sep=""),las=2)
}
  
```

Then we define a function to separate the times of day.
It probably could be done better, but I'll use a "single" clustering method calculated on the time in second.
For now, the user will have to define the number of relocation by day

```{r}
find_clustTOD <- function(ts_tab,nb_reloc=12)
{
  gp <- cutree(hclust(dist(ts_tab$time_s),method="single"),nb_reloc)
  meanTimeGp <- tapply(ts_tab$time_s,gp,mean)
  meanGp<-format(as.POSIXct(meanTimeGp,origin=today(tzone = "GMT"),tz="GMT"),"%H:%M")[order(meanTimeGp)]
  return(data.frame(gp_TOD=match(as.character(gp),names(meanGp)),
             meanGp=meanGp[as.character(gp)]
             ))
}
```


The idea of the find_clustTOD function is to classify the time of day which correspond to each relocation data in a normalized form.
Look at the following table and plot, to understand what it does:

```{r}
A <- cbind(list_dateTime$Zorro02,find_clustTOD(list_dateTime$Zorro02))
kable(head(A,25))
plot(A$date,A$gp_TOD,type="b",xlab="Date",ylab="Time of day group")
```

Then it is easy to create a function which calculate which TOD groups are missing and which are duplicated every day between start and end.

```{r}
mis_dup_TOD<-function(ts_tab_TOD){
  nbClusTOD<-max(ts_tab_TOD$gp_TOD)
  dupliTOD<-duplicated(ts_tab_TOD[c("date","gp_TOD")])
  minDate<-min(ts_tab_TOD$date)
  maxDate<-max(ts_tab_TOD$date)
  minDateTOD<-min(ts_tab_TOD$gp_TOD[ts_tab_TOD$date==minDate])
  maxDateTOD<-max(ts_tab_TOD$gp_TOD[ts_tab_TOD$date==maxDate])
  completeDateTOD<-rbind(data.frame(date=as.Date(minDate),gp_TOD=minDateTOD:nbClusTOD),
                        data.frame(date=as.Date(rep((minDate+1) : (maxDate-1), each=nbClusTOD), origin="1970-01-01"), gp_TOD=rep(1:nbClusTOD,length(rep((minDate+1) : (maxDate-1))))),
                        data.frame(date=maxDate,gp_TOD=1:maxDateTOD),deparse.level = 0)
  completeDateTOD$nb<-integer(nrow(completeDateTOD))
  for(i in 1:nrow(completeDateTOD))
    {completeDateTOD$nb[i]<-length(which(ts_tab_TOD$date==completeDateTOD$date[i] & ts_tab_TOD$gp_TOD==completeDateTOD$gp_TOD[i]))}
  return(completeDateTOD)
}
```


### Zorro02

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$Zorro02, "Zorro02")
```

There seem to be 12 different time of days in the data:

```{r}
list_dateTime$Zorro02<-cbind(list_dateTime$Zorro02, find_clustTOD(list_dateTime$Zorro02,12))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$Zorro02[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD<-list()
misRepTOD$Zorro02<-mis_dup_TOD(list_dateTime$Zorro02)
```

The missing time of day are:
```{r}
table(misRepTOD$Zorro02$gp_TOD[misRepTOD$Zorro02$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$Zorro02$nb[misRepTOD$Zorro02$nb>1],factor(misRepTOD$Zorro02$gp_TOD)[misRepTOD$Zorro02$nb>1])
```



### Zorro03

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$Zorro03, "Zorro03")
```

There seem to be 12 different time of days in the data:

```{r}
list_dateTime$Zorro03<-cbind(list_dateTime$Zorro03, find_clustTOD(list_dateTime$Zorro03,12))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$Zorro03[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD$Zorro03<-mis_dup_TOD(list_dateTime$Zorro03)
```

The missing time of day are:
```{r}
table(misRepTOD$Zorro03$gp_TOD[misRepTOD$Zorro03$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$Zorro03$nb[misRepTOD$Zorro03$nb>1],factor(misRepTOD$Zorro03$gp_TOD)[misRepTOD$Zorro03$nb>1])
```

### Zorro04

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$Zorro04, "Zorro04")
```

There seem to be 12 different time of days in the data:

```{r}
list_dateTime$Zorro04<-cbind(list_dateTime$Zorro04, find_clustTOD(list_dateTime$Zorro04,12))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$Zorro04[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD$Zorro04<-mis_dup_TOD(list_dateTime$Zorro04)
```

The missing time of day are:
```{r}
table(misRepTOD$Zorro04$gp_TOD[misRepTOD$Zorro04$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$Zorro04$nb[misRepTOD$Zorro04$nb>1],factor(misRepTOD$Zorro04$gp_TOD)[misRepTOD$Zorro04$nb>1])
```

### Zorro05

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$Zorro05, "Zorro05")
```

There seem to be 12 different time of days in the data:

```{r}
list_dateTime$Zorro05<-cbind(list_dateTime$Zorro05, find_clustTOD(list_dateTime$Zorro05,12))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$Zorro05[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD$Zorro05<-mis_dup_TOD(list_dateTime$Zorro05)
```

The missing time of day are:
```{r}
table(misRepTOD$Zorro05$gp_TOD[misRepTOD$Zorro05$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$Zorro05$nb[misRepTOD$Zorro05$nb>1],factor(misRepTOD$Zorro05$gp_TOD)[misRepTOD$Zorro05$nb>1])
```

### Zorro06

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$Zorro06, "Zorro06")
```

There seem to be 12 different time of days in the data:

```{r}
list_dateTime$Zorro06<-cbind(list_dateTime$Zorro06, find_clustTOD(list_dateTime$Zorro06,12))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$Zorro06[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD$Zorro06<-mis_dup_TOD(list_dateTime$Zorro06)
```

The missing time of day are:
```{r}
table(misRepTOD$Zorro06$gp_TOD[misRepTOD$Zorro06$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$Zorro06$nb[misRepTOD$Zorro06$nb>1],factor(misRepTOD$Zorro06$gp_TOD)[misRepTOD$Zorro06$nb>1])
```

### Zorro07

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$Zorro07, "Zorro07")
```

There seem to be 12 different time of days in the data:

```{r}
list_dateTime$Zorro07<-cbind(list_dateTime$Zorro07, find_clustTOD(list_dateTime$Zorro07,12))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$Zorro07[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD$Zorro07<-mis_dup_TOD(list_dateTime$Zorro07)
```

The missing time of day are:
```{r}
table(misRepTOD$Zorro07$gp_TOD[misRepTOD$Zorro07$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$Zorro07$nb[misRepTOD$Zorro07$nb>1],factor(misRepTOD$Zorro07$gp_TOD)[misRepTOD$Zorro07$nb>1])
```

### Guacharaca01

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$Guacharaca01, "Guacharaca01")
```

There seem to be 25 different time of days in the data:

```{r}
list_dateTime$Guacharaca01<-cbind(list_dateTime$Guacharaca01, find_clustTOD(list_dateTime$Guacharaca01,25))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$Guacharaca01[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD$Guacharaca01<-mis_dup_TOD(list_dateTime$Guacharaca01)
```

The missing time of day are:
```{r}
table(misRepTOD$Guacharaca01$gp_TOD[misRepTOD$Guacharaca01$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$Guacharaca01$nb[misRepTOD$Guacharaca01$nb>1],factor(misRepTOD$Guacharaca01$gp_TOD)[misRepTOD$Guacharaca01$nb>1])
```

### Guacharaca03

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$Guacharaca03, "Guacharaca03")
```

There seem to be 25 different time of days in the data:

```{r}
list_dateTime$Guacharaca03<-cbind(list_dateTime$Guacharaca03, find_clustTOD(list_dateTime$Guacharaca03,25))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$Guacharaca03[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD$Guacharaca03<-mis_dup_TOD(list_dateTime$Guacharaca03)
```

The missing time of day are:
```{r}
table(misRepTOD$Guacharaca03$gp_TOD[misRepTOD$Guacharaca03$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$Guacharaca03$nb[misRepTOD$Guacharaca03$nb>1],factor(misRepTOD$Guacharaca03$gp_TOD)[misRepTOD$Guacharaca03$nb>1])
```

### Phimosus01

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$Phimosus01, "Phimosus01")
```

There seem to be 48 different time of days in the data:

```{r}
list_dateTime$Phimosus01<-cbind(list_dateTime$Phimosus01, find_clustTOD(list_dateTime$Phimosus01,48))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$Phimosus01[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD$Phimosus01<-mis_dup_TOD(list_dateTime$Phimosus01)
```

The missing time of day are:
```{r}
table(misRepTOD$Phimosus01$gp_TOD[misRepTOD$Phimosus01$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$Phimosus01$nb[misRepTOD$Phimosus01$nb>1],factor(misRepTOD$Phimosus01$gp_TOD)[misRepTOD$Phimosus01$nb>1])
```

### Phimosus02

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$Phimosus02, "Phimosus02")
```

There seem to be 12 different time of days in the data:

```{r}
list_dateTime$Phimosus02<-cbind(list_dateTime$Phimosus02, find_clustTOD(list_dateTime$Phimosus02,48))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$Phimosus02[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD$Phimosus02<-mis_dup_TOD(list_dateTime$Phimosus02)
```

The missing time of day are:
```{r}
table(misRepTOD$Phimosus02$gp_TOD[misRepTOD$Phimosus02$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$Phimosus02$nb[misRepTOD$Phimosus02$nb>1],factor(misRepTOD$Phimosus02$gp_TOD)[misRepTOD$Phimosus02$nb>1])
```

### Pigua1

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$Pigua1, "Pigua1")
```

There seem to be 25 different time of days in the data:

```{r}
list_dateTime$Pigua1<-cbind(list_dateTime$Pigua1, find_clustTOD(list_dateTime$Pigua1,25))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$Pigua1[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD$Pigua1<-mis_dup_TOD(list_dateTime$Pigua1)
```

The missing time of day are:
```{r}
table(misRepTOD$Pigua1$gp_TOD[misRepTOD$Pigua1$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$Pigua1$nb[misRepTOD$Pigua1$nb>1],factor(misRepTOD$Pigua1$gp_TOD)[misRepTOD$Pigua1$nb>1])
```

### Zarigueya1

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$Zarigueya1, "Zarigueya1")
```

There seem to be 3 different time of days in the data:

```{r}
list_dateTime$Zarigueya1<-cbind(list_dateTime$Zarigueya1, find_clustTOD(list_dateTime$Zarigueya1,3))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$Zarigueya1[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD$Zarigueya1<-mis_dup_TOD(list_dateTime$Zarigueya1)
```

The missing time of day are:
```{r}
table(misRepTOD$Zarigueya1$gp_TOD[misRepTOD$Zarigueya1$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$Zarigueya1$nb[misRepTOD$Zarigueya1$nb>1],factor(misRepTOD$Zarigueya1$gp_TOD)[misRepTOD$Zarigueya1$nb>1])
```

### Zarigueya3

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$Zarigueya3, "Zarigueya3")
```

There seem to be 5 different time of days in the data:

```{r}
list_dateTime$Zarigueya3<-cbind(list_dateTime$Zarigueya3, find_clustTOD(list_dateTime$Zarigueya3,5))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$Zarigueya3[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD$Zarigueya3<-mis_dup_TOD(list_dateTime$Zarigueya3)
```

The missing time of day are:
```{r}
table(misRepTOD$Zarigueya3$gp_TOD[misRepTOD$Zarigueya3$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$Zarigueya3$nb[misRepTOD$Zarigueya3$nb>1],factor(misRepTOD$Zarigueya3$gp_TOD)[misRepTOD$Zarigueya3$nb>1])
```

### Zarigueya4

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$Zarigueya4, "Zarigueya4")
```

There seem to be 5 different time of days in the data:

```{r}
list_dateTime$Zarigueya4<-cbind(list_dateTime$Zarigueya4, find_clustTOD(list_dateTime$Zarigueya4,5))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$Zarigueya4[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD$Zarigueya4<-mis_dup_TOD(list_dateTime$Zarigueya4)
```

The missing time of day are:
```{r}
table(misRepTOD$Zarigueya4$gp_TOD[misRepTOD$Zarigueya4$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$Zarigueya4$nb[misRepTOD$Zarigueya4$nb>1],factor(misRepTOD$Zarigueya4$gp_TOD)[misRepTOD$Zarigueya4$nb>1])
```

### Phimosus04

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$Phimosus04, "Phimosus04")
```

There seem to be 48 different time of days in the data:

```{r}
list_dateTime$Phimosus04<-cbind(list_dateTime$Phimosus04, find_clustTOD(list_dateTime$Phimosus04,48))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$Phimosus04[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD$Phimosus04<-mis_dup_TOD(list_dateTime$Phimosus04)
```

The missing time of day are:
```{r}
table(misRepTOD$Phimosus04$gp_TOD[misRepTOD$Phimosus04$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$Phimosus04$nb[misRepTOD$Phimosus04$nb>1],factor(misRepTOD$Phimosus04$gp_TOD)[misRepTOD$Phimosus04$nb>1])
```

### Pigua2

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$Pigua2, "Pigua2")
```

There seem to be 25 different time of days in the data:

```{r}
list_dateTime$Pigua2<-cbind(list_dateTime$Pigua2, find_clustTOD(list_dateTime$Pigua2,25))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$Pigua2[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD$Pigua2<-mis_dup_TOD(list_dateTime$Pigua2)
```

The missing time of day are:
```{r}
table(misRepTOD$Pigua2$gp_TOD[misRepTOD$Pigua2$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$Pigua2$nb[misRepTOD$Pigua2$nb>1],factor(misRepTOD$Pigua2$gp_TOD)[misRepTOD$Pigua2$nb>1])
```

### Garza1

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$Garza1, "Garza1")
```

There seem to be 72 different time of days in the data:

```{r}
list_dateTime$Garza1<-cbind(list_dateTime$Garza1, find_clustTOD(list_dateTime$Garza1,72))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$Garza1[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD$Garza1<-mis_dup_TOD(list_dateTime$Garza1)
```

The missing time of day are:
```{r}
table(misRepTOD$Garza1$gp_TOD[misRepTOD$Garza1$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$Garza1$nb[misRepTOD$Garza1$nb>1],factor(misRepTOD$Garza1$gp_TOD)[misRepTOD$Garza1$nb>1])
```

### GarzaAve4

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$GarzaAve4, "GarzaAve4")
```

There seem to be 25 different time of days in the data:

```{r}
list_dateTime$GarzaAve4<-cbind(list_dateTime$GarzaAve4, find_clustTOD(list_dateTime$GarzaAve4,25))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$GarzaAve4[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD$GarzaAve4<-mis_dup_TOD(list_dateTime$GarzaAve4)
```

The missing time of day are:
```{r}
table(misRepTOD$GarzaAve4$gp_TOD[misRepTOD$GarzaAve4$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$GarzaAve4$nb[misRepTOD$GarzaAve4$nb>1],factor(misRepTOD$GarzaAve4$gp_TOD)[misRepTOD$GarzaAve4$nb>1])
```

### Zarigueya5

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$Zarigueya5, "Zarigueya5")
```

There seem to be 6 different time of days in the data:

```{r}
list_dateTime$Zarigueya5<-cbind(list_dateTime$Zarigueya5, find_clustTOD(list_dateTime$Zarigueya5,6))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$Zarigueya5[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD$Zarigueya5<-mis_dup_TOD(list_dateTime$Zarigueya5)
```

The missing time of day are:
```{r}
table(misRepTOD$Zarigueya5$gp_TOD[misRepTOD$Zarigueya5$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$Zarigueya5$nb[misRepTOD$Zarigueya5$nb>1],factor(misRepTOD$Zarigueya5$gp_TOD)[misRepTOD$Zarigueya5$nb>1])
```

### Pigua5

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$Pigua5, "Pigua5")
```

There seem to be 27 different time of days in the data:

```{r}
list_dateTime$Pigua5<-cbind(list_dateTime$Pigua5, find_clustTOD(list_dateTime$Pigua5,27))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$Pigua5[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD$Pigua5<-mis_dup_TOD(list_dateTime$Pigua5)
```

The missing time of day are:
```{r}
table(misRepTOD$Pigua5$gp_TOD[misRepTOD$Pigua5$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$Pigua5$nb[misRepTOD$Pigua5$nb>1],factor(misRepTOD$Pigua5$gp_TOD)[misRepTOD$Pigua5$nb>1])
```

### Guacharaca06

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$Guacharaca06, "Guacharaca06")
```

There seem to be 27 different time of days in the data:

```{r}
list_dateTime$Guacharaca06<-cbind(list_dateTime$Guacharaca06, find_clustTOD(list_dateTime$Guacharaca06,27))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$Guacharaca06[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD$Guacharaca06<-mis_dup_TOD(list_dateTime$Guacharaca06)
```

The missing time of day are:
```{r}
table(misRepTOD$Guacharaca06$gp_TOD[misRepTOD$Guacharaca06$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$Guacharaca06$nb[misRepTOD$Guacharaca06$nb>1],factor(misRepTOD$Guacharaca06$gp_TOD)[misRepTOD$Guacharaca06$nb>1])
```

### Ardilla1

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$Ardilla1, "Ardilla1")
```

There seem to be 9 different time of days in the data:

```{r}
list_dateTime$Ardilla1<-cbind(list_dateTime$Ardilla1, find_clustTOD(list_dateTime$Ardilla1,9))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$Ardilla1[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD$Ardilla1<-mis_dup_TOD(list_dateTime$Ardilla1)
```

The missing time of day are:
```{r}
table(misRepTOD$Ardilla1$gp_TOD[misRepTOD$Ardilla1$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$Ardilla1$nb[misRepTOD$Ardilla1$nb>1],factor(misRepTOD$Ardilla1$gp_TOD)[misRepTOD$Ardilla1$nb>1])
```

### GarzaAve2

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$GarzaAve2, "GarzaAve2")
```

There seem to be 48 different time of days in the data:

```{r}
list_dateTime$GarzaAve2<-cbind(list_dateTime$GarzaAve2, find_clustTOD(list_dateTime$GarzaAve2,48))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$GarzaAve2[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD$GarzaAve2<-mis_dup_TOD(list_dateTime$GarzaAve2)
```

The missing time of day are:
```{r}
table(misRepTOD$GarzaAve2$gp_TOD[misRepTOD$GarzaAve2$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$GarzaAve2$nb[misRepTOD$GarzaAve2$nb>1],factor(misRepTOD$GarzaAve2$gp_TOD)[misRepTOD$GarzaAve2$nb>1])
```

### GarzaAve3

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$GarzaAve3, "GarzaAve3")
```

There seem to be 48 different time of days in the data:

```{r}
list_dateTime$GarzaAve3<-cbind(list_dateTime$GarzaAve3, find_clustTOD(list_dateTime$GarzaAve3,48))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$GarzaAve3[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD$GarzaAve3<-mis_dup_TOD(list_dateTime$GarzaAve3)
```

The missing time of day are:
```{r}
table(misRepTOD$GarzaAve3$gp_TOD[misRepTOD$GarzaAve3$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$GarzaAve3$nb[misRepTOD$GarzaAve3$nb>1],factor(misRepTOD$GarzaAve3$gp_TOD)[misRepTOD$GarzaAve3$nb>1])
```

### Zarigueya6

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$Zarigueya6, "Zarigueya6")
```

There seem to be 5 different time of days in the data:

```{r}
list_dateTime$Zarigueya6<-cbind(list_dateTime$Zarigueya6, find_clustTOD(list_dateTime$Zarigueya6,5))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$Zarigueya6[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD$Zarigueya6<-mis_dup_TOD(list_dateTime$Zarigueya6)
```

The missing time of day are:
```{r}
table(misRepTOD$Zarigueya6$gp_TOD[misRepTOD$Zarigueya6$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$Zarigueya6$nb[misRepTOD$Zarigueya6$nb>1],factor(misRepTOD$Zarigueya6$gp_TOD)[misRepTOD$Zarigueya6$nb>1])
```

### Phimosus05

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$Phimosus05, "Phimosus05")
```

There seem to be 27 different time of days in the data:

```{r}
list_dateTime$Phimosus05<-cbind(list_dateTime$Phimosus05, find_clustTOD(list_dateTime$Phimosus05,27))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$Phimosus05[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD$Phimosus05<-mis_dup_TOD(list_dateTime$Phimosus05)
```

The missing time of day are:
```{r}
table(misRepTOD$Phimosus05$gp_TOD[misRepTOD$Phimosus05$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$Phimosus05$nb[misRepTOD$Phimosus05$nb>1],factor(misRepTOD$Phimosus05$gp_TOD)[misRepTOD$Phimosus05$nb>1])
```

### Phimosus07

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$Phimosus07, "Phimosus07")
```

There seem to be 27 different time of days in the data:

```{r}
list_dateTime$Phimosus07<-cbind(list_dateTime$Phimosus07, find_clustTOD(list_dateTime$Phimosus07,27))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$Phimosus07[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD$Phimosus07<-mis_dup_TOD(list_dateTime$Phimosus07)
```

The missing time of day are:
```{r}
table(misRepTOD$Phimosus07$gp_TOD[misRepTOD$Phimosus07$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$Phimosus07$nb[misRepTOD$Phimosus07$nb>1],factor(misRepTOD$Phimosus07$gp_TOD)[misRepTOD$Phimosus07$nb>1])
```

### Phimosus06

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$Phimosus06, "Phimosus06")
```

There seem to be 27 different time of days in the data:

```{r}
list_dateTime$Phimosus06<-cbind(list_dateTime$Phimosus06, find_clustTOD(list_dateTime$Phimosus06,27))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$Phimosus06[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD$Phimosus06<-mis_dup_TOD(list_dateTime$Phimosus06)
```

The missing time of day are:
```{r}
table(misRepTOD$Phimosus06$gp_TOD[misRepTOD$Phimosus06$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$Phimosus06$nb[misRepTOD$Phimosus06$nb>1],factor(misRepTOD$Phimosus06$gp_TOD)[misRepTOD$Phimosus06$nb>1])
```

### Zarigueya7

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$Zarigueya7, "Zarigueya7")
```

There seem to be 6 different time of days in the data:

```{r}
list_dateTime$Zarigueya7<-cbind(list_dateTime$Zarigueya7, find_clustTOD(list_dateTime$Zarigueya7,6))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$Zarigueya7[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD$Zarigueya7<-mis_dup_TOD(list_dateTime$Zarigueya7)
```

The missing time of day are:
```{r}
table(misRepTOD$Zarigueya7$gp_TOD[misRepTOD$Zarigueya7$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$Zarigueya7$nb[misRepTOD$Zarigueya7$nb>1],factor(misRepTOD$Zarigueya7$gp_TOD)[misRepTOD$Zarigueya7$nb>1])
```

### Guacharaca02

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$Guacharaca02, "Guacharaca02")
```

There seem to be 27 different time of days in the data:

```{r}
list_dateTime$Guacharaca02<-cbind(list_dateTime$Guacharaca02, find_clustTOD(list_dateTime$Guacharaca02,27))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$Guacharaca02[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD$Guacharaca02<-mis_dup_TOD(list_dateTime$Guacharaca02)
```

The missing time of day are:
```{r}
table(misRepTOD$Guacharaca02$gp_TOD[misRepTOD$Guacharaca02$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$Guacharaca02$nb[misRepTOD$Guacharaca02$nb>1],factor(misRepTOD$Guacharaca02$gp_TOD)[misRepTOD$Guacharaca02$nb>1])
```

### PavaGarza-4

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$`PavaGarza-4`, "`PavaGarza-4`")
```

There seem to be 38 different time of days in the data:

```{r}
list_dateTime$`PavaGarza-4`<-cbind(list_dateTime$`PavaGarza-4`, find_clustTOD(list_dateTime$`PavaGarza-4`,38))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$`PavaGarza-4`[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD$`PavaGarza-4`<-mis_dup_TOD(list_dateTime$`PavaGarza-4`)
```

The missing time of day are:
```{r}
table(misRepTOD$`PavaGarza-4`$gp_TOD[misRepTOD$`PavaGarza-4`$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$`PavaGarza-4`$nb[misRepTOD$`PavaGarza-4`$nb>1],factor(misRepTOD$`PavaGarza-4`$gp_TOD)[misRepTOD$`PavaGarza-4`$nb>1])
```

### Asio2

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$Asio2, "Asio2")
```

There seem to be 9 different time of days in the data:

```{r}
list_dateTime$Asio2<-cbind(list_dateTime$Asio2, find_clustTOD(list_dateTime$Asio2,9))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$Asio2[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD$Asio2<-mis_dup_TOD(list_dateTime$Asio2)
```

The missing time of day are:
```{r}
table(misRepTOD$Asio2$gp_TOD[misRepTOD$Asio2$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$Asio2$nb[misRepTOD$Asio2$nb>1],factor(misRepTOD$Asio2$gp_TOD)[misRepTOD$Asio2$nb>1])
```

### BuhoPigua6

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$BuhoPigua6, "BuhoPigua6")
```

There seem to be 16 different time of days in the data:

```{r}
list_dateTime$BuhoPigua6<-cbind(list_dateTime$BuhoPigua6, find_clustTOD(list_dateTime$BuhoPigua6,16))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$BuhoPigua6[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD$BuhoPigua6<-mis_dup_TOD(list_dateTime$BuhoPigua6)
```

The missing time of day are:
```{r}
table(misRepTOD$BuhoPigua6$gp_TOD[misRepTOD$BuhoPigua6$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$BuhoPigua6$nb[misRepTOD$BuhoPigua6$nb>1],factor(misRepTOD$BuhoPigua6$gp_TOD)[misRepTOD$BuhoPigua6$nb>1])
```

### Guacharaca04

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$Guacharaca04, "Guacharaca04")
```

There seem to be 3 different time of days in the data:

```{r}
list_dateTime$Guacharaca04<-cbind(list_dateTime$Guacharaca04, find_clustTOD(list_dateTime$Guacharaca04,3))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$Guacharaca04[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD$Guacharaca04<-mis_dup_TOD(list_dateTime$Guacharaca04)
```

The missing time of day are:
```{r}
table(misRepTOD$Guacharaca04$gp_TOD[misRepTOD$Guacharaca04$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$Guacharaca04$nb[misRepTOD$Guacharaca04$nb>1],factor(misRepTOD$Guacharaca04$gp_TOD)[misRepTOD$Guacharaca04$nb>1])
```

### PerezosoZorro1

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$PerezosoZorro1, "PerezosoZorro1")
```

There seem to be 3 different time of days in the data:

```{r}
list_dateTime$PerezosoZorro1<-cbind(list_dateTime$PerezosoZorro1, find_clustTOD(list_dateTime$PerezosoZorro1,3))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$PerezosoZorro1[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD$PerezosoZorro1<-mis_dup_TOD(list_dateTime$PerezosoZorro1)
```

The missing time of day are:
```{r}
table(misRepTOD$PerezosoZorro1$gp_TOD[misRepTOD$PerezosoZorro1$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$PerezosoZorro1$nb[misRepTOD$PerezosoZorro1$nb>1],factor(misRepTOD$PerezosoZorro1$gp_TOD)[misRepTOD$PerezosoZorro1$nb>1])
```

### Titi4

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$Titi4, "Titi4")
```

There seem to be 16 different time of days in the data:

```{r}
list_dateTime$Titi4<-cbind(list_dateTime$Titi4, find_clustTOD(list_dateTime$Titi4,16))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$Titi4[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD$Titi4<-mis_dup_TOD(list_dateTime$Titi4)
```

The missing time of day are:
```{r}
table(misRepTOD$Titi4$gp_TOD[misRepTOD$Titi4$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$Titi4$nb[misRepTOD$Titi4$nb>1],factor(misRepTOD$Titi4$gp_TOD)[misRepTOD$Titi4$nb>1])
```

### Phimosus03

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$Phimosus03, "Phimosus03")
```

There seem to be 16 different time of days in the data:

```{r}
list_dateTime$Phimosus03<-cbind(list_dateTime$Phimosus03, find_clustTOD(list_dateTime$Phimosus03,16))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$Phimosus03[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD$Phimosus03<-mis_dup_TOD(list_dateTime$Phimosus03)
```

The missing time of day are:
```{r}
table(misRepTOD$Phimosus03$gp_TOD[misRepTOD$Phimosus03$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$Phimosus03$nb[misRepTOD$Phimosus03$nb>1],factor(misRepTOD$Phimosus03$gp_TOD)[misRepTOD$Phimosus03$nb>1])
```

### GuacharacaAsio-4

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$`GuacharacaAsio-4`, "GuacharacaAsio-4")
```

There seem to be 9 different time of days in the data:

```{r}
list_dateTime$`GuacharacaAsio-4`<-cbind(list_dateTime$`GuacharacaAsio-4`, find_clustTOD(list_dateTime$`GuacharacaAsio-4`,9))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$`GuacharacaAsio-4`[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD$`GuacharacaAsio-4`<-mis_dup_TOD(list_dateTime$`GuacharacaAsio-4`)
```

The missing time of day are:
```{r}
table(misRepTOD$`GuacharacaAsio-4`$gp_TOD[misRepTOD$`GuacharacaAsio-4`$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$`GuacharacaAsio-4`$nb[misRepTOD$`GuacharacaAsio-4`$nb>1],factor(misRepTOD$`GuacharacaAsio-4`$gp_TOD)[misRepTOD$`GuacharacaAsio-4`$nb>1])
```

### GarzaTiti3

```{r fig.height=10}
par(mfrow=c(2,1))
hists_timestamps(list_dateTime$GarzaTiti3, "GarzaTiti3")
```

There seem to be 15 different time of days in the data:

```{r}
list_dateTime$GarzaTiti3<-cbind(list_dateTime$GarzaTiti3, find_clustTOD(list_dateTime$GarzaTiti3,15))
```

The average time of the clustered TOD are:

```{r}
A<-unique(list_dateTime$GarzaTiti3[c("gp_TOD","meanGp")])
A[order(A$gp_TOD),]%>%kable(row.names = F)
```



Concerning repeated and missing times of day:

```{r}
misRepTOD$GarzaTiti3<-mis_dup_TOD(list_dateTime$GarzaTiti3)
```

The missing time of day are:
```{r}
table(misRepTOD$GarzaTiti3$gp_TOD[misRepTOD$GarzaTiti3$nb==0])
```

The repeated time of day are:

```{r}
table(misRepTOD$GarzaTiti3$nb[misRepTOD$GarzaTiti3$nb>1],factor(misRepTOD$GarzaTiti3$gp_TOD)[misRepTOD$GarzaTiti3$nb>1])
```

# Saving the objects created here

```{r}
save(list=c("list_dateTime","misRepTOD"),file="list_dateTime.RData")
```


